---
title: "ReAnalysis Table"
author: "CT"
date: "Thursday, December  05, 2016"
output:
  word_document: default
  html_document: default
note: Re analysis after  merged weather, calculated Tt, re calculate the TT for mid
  flowering .
---

AIM:

- Adjust Tt to 50% flow across all datasets
- Show variability in Tt to flower in all datasets
- Explore relative differences in TT flow among cultivars

Steps:
- This script reads the file created in previous script (script 3 where the TT to flower was adjusted to 50% ). Normalisation of TT to flower.
- Graph the days and TTAdj50Flo (TT adjusted to 50% Flowering) by location and cultivar (explore location and cultivar effects )
- First the effect of genoytpe is explored: same environment with different genotypes  
- Old removed: Then in the second part it selects a subset of data to explore the effect of seasonality. Same genotypes in different envrionments.

```{r, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(here)
```

```{r}
print(paste0("Here is: ", here()))
```


```{r}
chapterPath <- paste0(here(),"/Chapter_03") 
rawPath <- paste0(chapterPath,"/Data/RawData/")
workDPath <- paste0(chapterPath,"/Data/WorkedData/")
```



```{r   loadFile}

#get dataframe created in ReAnalysis1
df_Rea3 <-read.table(paste0(workDPath,"df_Rea3.txt"),header=TRUE)


#head(df_Data)

summary(df_Rea3)

```

Use slope values (Rea3) to normalise TT flowering 
Here select only dataset with 50% flowering now that is adjusted (remove Dear et al 5 and 100 to avoid repeated calculation )

373 rows decrease to (373 - 28 x2)=317 (filter out )

```{r}
#Flowering reference = Floref
floref <- 50

TTpercflo <- 2.17 # oCd per % flowering (value calculated from DearEtAL1993_Reanalysis3 script 1 oCd /0.45 % flower)

df_Rea4 <- df_Rea3 %>%
  mutate(TTFloAdj=((floref-PercentFlower)*TTpercflo)+TTtoFlower) %>%
    mutate(Out=factor(paste0(AuthorYear,"_",PercentFlower))) %>%
  filter(Out!= as.character("DearEtal1993_5")) %>%
  filter(Out!= as.character("DearEtal1993_100"))

summary(df_Rea4)
```

should recalculate Dear et al again ? It should be the same TTtoflower = TTFloAdj ! FIXME .

```{r}
#graph TTtoFlower vs TTFloAdj
#Check TT 
df_Rea4  %>% 
ggplot(aes(x=TTtoFlower, y= TTFloAdj)) +
    geom_point(shape=21)+
  xlim(500,2800)+
  geom_abline(intercept = 0, slope = 1)

```


plot TTadj vs. sowing date

```{r , fig.height=5, fig.width=10, include=FALSE}
df_Rea4  %>% 
  filter(Treatcultivar=="Trikkala"|
         Treatcultivar=="Dalkeith"|
           Treatcultivar=="Woogenellup"| 
           Treatcultivar=="MtBarker") %>%
ggplot(aes(x=month(SowingDate), y= TTFloAdj, colour=Treatcultivar)) +
    geom_point(shape=21) +
  scale_x_continuous(breaks = c(2,4,6,8,10,12) )+
  #scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") 
  geom_smooth()
  #facet_grid(Country~.)
```


Graph days to Flower and TTAdj vs. Location 


```{r,fig.height=5, fig.width=10, include=FALSE}
library(scales)
df_Rea4  %>% 
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  #use this filter to analyse single locations
  #filter (Location=="Whatawhata")%>%
  ggplot(aes(x=Location, y= Value, colour=Treatcultivar)) +
  geom_point(shape=21) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
 theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")
```

Find values among NZ and Aus for text

```{r}
df_Rea4 %>%
  dplyr::select(Country,DaysToFlower,TTFloAdj) %>%
  tidyr::gather("VarName","VarValue", DaysToFlower:TTFloAdj) %>%
  group_by(Country, VarName) %>%
  summarise_each(funs(mean)) %>%
  tidyr::spread(Country,VarValue)  %>%
  mutate(Diff=round(NZ-AU,0)) %>%
  mutate(Diff_rel=round(Diff/NZ*100,0))
```
Min and Max for text

```{r}
df_Rea4 %>%
  dplyr::select(Country,DaysToFlower,TTFloAdj) %>%
  tidyr::gather("VarName","VarValue",DaysToFlower:TTFloAdj) %>%
  group_by(Country, VarName) %>%
 summarise_each(funs(min,max)) 
```

Show total variability per location

```{r, fig.height=8 , fig.width= 20}
df_Rea4 %>%
  dplyr::select(LocationYear:Treatcultivar,DaysToFlower,TTtoFlower,Country) %>%
  gather("VarName","VarValue",DaysToFlower:TTtoFlower)  %>%
  mutate(VarName=factor(VarName, level=c("DaysToFlower","TTtoFlower"),labels=c("Days to flower","Thermal-time to flowering (oCd)"))) %>%
    mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
#  ggplot(aes(x=reorder(Month,month(SowingDate)), y=DaysToFlower)) +
  #filter(Treatcultivar=="MtBarker") %>%
  ggplot(aes(x= reorder(Location,VarValue), y=VarValue))+
  geom_boxplot(alpha=0.2)+
  #geom_jitter(size=3,alpha=0.7,width = 0.1, aes(colour=reorder(Month,month(SowingDate)),shape=reorder(Month,month(SowingDate))))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  geom_jitter(size=3,alpha=0.7,width = 0.1, aes(shape= Country, colour=reorder(Month,month(SowingDate))))+
  #theme(legend.position="none")+
  labs(x="Experiment location", y="Time to flower")+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 9))+
  theme(axis.text.y=element_text(size= 18))+
  theme_bw(base_size=18)+
    facet_grid(.~VarName, scales="free") +
 # facet_wrap(~VarName, scales="free") +
  coord_flip() + theme(legend.position="top") + guides(colour=guide_legend(title="Sowing month"))
ggsave(paste0(workDPath,"ch03_06_DaysTTFlowerLocation.tiff"),width=12, height=6, dpi=300)

```

Then select Contrasting cultivars to compare : eg: Trikkala, Tallarook, MtBarker

```{r,fig.height=5, fig.width=10, include=FALSE}

library(scales)
df_Rea4  %>% 
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  filter(Treatcultivar=="Trikkala"| 
           Treatcultivar=="Nungarin"|
           Treatcultivar=="Denmark"|
           Treatcultivar=="MtBarker"|
           Treatcultivar=="Bena"|
           Treatcultivar=="Tallarook"|
           Treatcultivar=="Dalkeith") %>%
  ggplot(aes(x=Location, y= Value, colour=Treatcultivar)) +
  geom_boxplot(alpha=0.2)+
  geom_jitter(width = 0.1, aes(colour=Treatcultivar))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
 #theme(legend.position="none")+
  labs(x=" Location", y="    oCd        Days")+
  facet_grid(Variable~Country, scales = "free")

summary (df_Rea4)

```

## This graph displays the TTAdjo50Flo!! 

```{r}
str(df_Rea4)
```

This graph shows the relative days and TT having the minimum time to flower. The aim is to show the difference of genotypes. (GENOTYPE EFFECT)

```{r, fig.height=12 , fig.width= 25}


# Find minimum avalues per 
df_min_vals <- df_Rea4  %>%
   mutate(SD_LOC = paste0(Location,"_",SowingDate)) %>%
   mutate(DaysToFlower_min=DaysToFlower,TTtoFlower_min=TTtoFlower) %>%
  dplyr::select(-DaysToFlower,-TTtoFlower)%>%
   dplyr::select(SD_LOC,DaysToFlower_min,TTtoFlower_min) %>%
   group_by(SD_LOC) %>%
   summarise_all(funs(min))

df_rel_gen <- df_Rea4 %>%
  mutate(SD_LOC = paste0(Location,"_",SowingDate)) %>%
  merge(df_min_vals,by=c("SD_LOC")) %>%
  mutate(DaysToFlower_norm=DaysToFlower-DaysToFlower_min,TTtoFlower_norm=TTtoFlower-TTtoFlower_min) %>%
  dplyr::select(LocationYear:Treatcultivar,DaysToFlower_norm,TTtoFlower_norm,Country, SD_LOC) %>%
  filter(Location!="Melbourne",Location!="ShentonPark" ) %>%
  filter(SowingDate !="1985-06-20")%>%
  filter(Treatcultivar=="Trikkala"| 
           Treatcultivar=="Nungarin"|
           Treatcultivar=="Denmark"|
           Treatcultivar=="MtBarker"|
           Treatcultivar=="Bena"|
           Treatcultivar=="Tallarook"|
           Treatcultivar=="Woogenellup"|
           Treatcultivar=="SeatonPark"|
           Treatcultivar=="Larisa"|
           Treatcultivar=="Dalkeith") %>%
  gather("VarName","VarValue",DaysToFlower_norm:TTtoFlower_norm)  %>%
  mutate(VarName=factor(VarName, level=c("DaysToFlower_norm","TTtoFlower_norm"),
                        labels=c("Days to flower", "Thermal time (oCd)"))) %>%
   mutate(Month=format(as.Date(ymd(SowingDate)),"%b"))

  
summary(df_rel_gen)

```

## Find minimum values per location/year/variable




```{r, fig.height=12 , fig.width= 25}

fs<-24

  df_rel_gen %>%
  ggplot(aes(x=reorder(SD_LOC,VarValue), y=VarValue))+
   geom_line(size=4,alpha=0.1,aes(colour=Country))+  
   geom_point(size=5,alpha=0.7, aes(shape= Country, colour=Treatcultivar))+
   labs(x="Location and sowing date", y="Difference in time to flower among cultivars")+
  theme(axis.text.y=element_text(size= fs))+
  theme_bw(base_size=18) +
  facet_grid(VarName~., scales="free") +
  theme(legend.position="top") + guides(colour=guide_legend(title="Cultivar ")) +
  theme(axis.text.x=element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size= fs))

ggsave(paste0(workDPath,"ch03_07_DaysTtGenotype.tiff"),width=25, height=12, dpi=300)
```

Here find maximum and mininum values days and tt among cultivars to use in text.

```{r}
df_rel_gen %>%
  group_by(VarName) %>%
  dplyr::select(VarName,VarValue) %>%
  summarise(min=min(VarValue), max=max(VarValue))
```

Save a dataset with corrected Tt to 50% flowering

```{r}
write.table(df_Rea4,paste0(workDPath, "df_Rea4_Ttadj.txt")) # FIXME: data need to be saved with clear/EXPLANATORY NAME .... NOT only a NUMBER!!!!!!!
```

