---
title: "R Notebook"
output: html_notebook
---

##Aim:

- Reads raw data weather all trials
- Check the data
- Graph temperature and Pp
- Calculates TT accumulation
- Saves technically consistent data


```{r, warning=FALSE}
library(here)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
```


```{r}
print(paste0("Here is: ", here()))
chapterPath <- paste0(here(),"/Chapter_03") 
rawPath <- paste0(chapterPath,"/Data/RawData/")
workDPath <- paste0(chapterPath,"/Data/WorkedData/")
```

fhgfgf


```{r}
#create file
df_We <- read.table(paste0(rawPath,"RawWeather.txt"),header=TRUE)

#head(df_We)

summary(df_We)
```

##Graph it

```{r,fig.height=10, fig.width=10}
df_We %>%
  mutate(Date=dmy(df_We$Date)) %>%
  filter(LocationYear != "Mininera2005") %>%
  tidyr::gather("Variable", "Value",Tx:Pp) %>%
 #mutate(Month=format(as.Date(dmy(as.character(Date))),"%b")) %>%
  ggplot(aes(x=Date,y=Value))+
  geom_line(aes(colour=Variable)) +
  facet_wrap(~LocationYear,scale="free") +
  labs(x=" Date", y=" degree Celsius/hours  ")+
  scale_color_manual(values=c("#333333", "#9999CC", "#CC3300"))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(labels = date_format("%b-%Y"))

ggsave(paste0(workDPath,"ch03_01_ReanTempPp.tiff"),width=8, height=8,dpi = 300)


```

## Define Tt cardinal temperatures

Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 40
REFS: MonksEtAl2009	,LonatiEtAl2009	,MootEtal2003, SilsburyetAl1984. 
							

```{r}
s<-18
tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  #labs(x="Temperature (degree Celsius)")+
  #labs(y="Thermal Time (oCd)") +
  geom_line()+
  theme_bw()+
  ylim(0,16)+
xlab(expression(Temperature~"("^"o"*"C)"))+
  ylab(expression(Thermal~Time~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text( size= s))+
  theme(axis.title.x=element_text( size= s))+
  theme(axis.text.y=element_text( size= s))+
  theme(axis.title.y=element_text(size= s))

ggsave(paste0(workDPath,"ch03_02_TtCalcModel.tiff"),width=12, height=8,dpi = 300)

```

#Create and test interpolation function - Test if works 

```{r}

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)



```

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

```{r}

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2 + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
   # print(TT_tn)
    
    }
 
   TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,24)

```
Calculate TT 

- Compares with simple method to calculate Tt with base temperature of 0oC

```{r}
df_We_tt <- df_We %>%
  mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s-TTday))

summary(df_We_tt)


```


```{r}
#Check TT  two methods : TTday_s = simple method (Tmean - Tbzero)
df_We_tt  %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
  geom_point(shape=21,alpha=0.2,colour='red')+
  geom_abline(intercept = 0, slope = 1)

```


```{r}
str(df_We_tt)
```


```{r}

ly<-unique(df_We_tt$LocationYear)
df_CumTT<-data.frame()
for(i in 1:length(ly)) {
  
  dfsub<-df_We_tt%>%filter(LocationYear==ly[i])%>%
    arrange(Date)%>%
    mutate(SumTTday = cumsum(TTday)) %>%  
    mutate(MinDate=min(Date))%>%mutate(DayCount=as.numeric(Date-MinDate))

  df_CumTT<-rbind(df_CumTT,dfsub)
  dfsub<-NULL
}

summary( df_CumTT)
```

# #Calculate accumulated Themal time 

```{r}

head(df_CumTT)
```

#Graph the accumulate TT 
```{r}

df_CumTT %>%
  ggplot(aes(x=DayCount,y=SumTTday))+
  geom_line(aes(colour=LocationYear, linetype=Country)) +
  #facet_wrap(~LocationYear,scale="free") +
  xlim(0,max(df_CumTT$DayCount))+
  ylim(0,max(df_CumTT$SumTTday))+
  facet_grid(.~Country)


```



```{r}
write.table(df_CumTT,paste0(workDPath, "df_CumTT.txt"))
```





